\documentclass[a4,11pt]{article}
\usepackage[a4paper,left=2.54cm,right=2.54cm,bottom=3cm,top=3cm,text={18cm,20cm},footskip=32pt]{geometry}
\usepackage{latexsym} 
\usepackage{amsmath} 
\usepackage{amsthm}	% per la stilizzazione dei teoremi e per gestire extra simboli matematici, size, space, font, etc..
\usepackage{amsopn}	% per stilizzazione di alcuni operatori matematici (e.g. lim e log)
\usepackage{amscd}	% per gestire frecce e circolarità tramite frecce su più livelli in un'equazione (tipo grafi)
\usepackage{amssymb} % per i simboli matematici
\usepackage{array}	% per creare e gestire array
\usepackage{actuarialsymbol} % per simboli attuariali e di matematica finanziaria 
\usepackage{mathtools} 
\usepackage{makeidx} 
\usepackage{multicol} 
\usepackage{multirow} 
\usepackage{caption} 
\captionsetup[figure]{font=footnotesize}
\usepackage{float} 
\usepackage{enumerate} 
\usepackage{graphicx}  
\usepackage{subfig} 
\usepackage{booktabs} 
\usepackage{color} 
\usepackage[english]{babel} 
\usepackage{wasysym}
\usepackage{appendix} % per inserire appendice
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{collref}
\usepackage{microtype} \graphicspath{ {Figures/}} 
\usepackage{lmodern}
\usepackage{soul}
\usepackage{bm}
\usepackage{bookmark}
\usepackage[authoryear]{natbib}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}

\title{Leveraging deep neural networks to estimate age specific mortality from life expectancy at birth}



\author[1]{Andrea Nigri}
\author[2]{Susanna Levantesi}
\author[3,4]{Jos\'e Manuel Aburto}

\affil[1]{\footnotesize Department of Agricultural Sciences, Food, Natural Resources and Engineering, University of Foggia. andrea.nigri@unifg.it}
\affil[2]{\footnotesize Department of Statistics, Sapienza University of Rome. susanna.levantesi@uniroma1.it}
\affil[3]{\footnotesize Leverhulme Centre for Demographic Science, Department of Sociology and Nuffield College at University of Oxford. jose-manuel.aburto@sociology.ox.ac.uk}
\affil[4]{\footnotesize Interdisciplinary Centre on Population Dynamics, University of Southern Denmark}


%\date{\today}

\begin{document}
	\maketitle

\noindent
\textbf{Funding:} JMA acknowledges support from the British Academy Newton International Fellowship NIFBA19/190679, Leverhulme Trust Large Centre Grant and the Interdisciplinary Centre for Population Dynamics at University of Southern Denmark.\\

\noindent
\textbf{Authors contributions:} AN conceived the idea. AN and JMA developed the methodology. AN wrote the code and performed the computations. AN and SL drafted the first version of the manuscript. JMA supervised the findings of this work.  All authors discussed the results and contributed to writing and editing the final manuscript.\\

\noindent
\textbf{Acknowledgements:} We thank Charles Rahal, Mark Verhagen, as well as N anonymous reviewers, for their useful discussions and comments on previous versions of this work.

\end{document}
